\begin{thebibliography}{1}

%\bibitem{example}
%N. Surname, ``Paper's name'',
%\emph{source / where it can be found}.

\bibitem{brief_intro}
S. Bansal, Mo Chen, S. Herbert and C. J. Tomlin, ``Hamilton-Jacobi Reachability: A Brief Overview and Recent Advances'',
\emph{arxiv.org/abs/1709.07523}.

\bibitem{reach_avoid_no_dist}
K. Margellos and J. Lygeros, ``Hamilton-Jacobi formulation for reach-avoid problems with an application to air traffic management'',
\emph{Proceedings of the 2010 American Control Conference}, 2010, pp. 3045-3050, doi: 10.1109/ACC.2010.5530514.

\bibitem{reach_avoid_with_dist}
K. Margellos and J. Lygeros, ``Hamilton–Jacobi Formulation for Reach–Avoid Differential Games,''
\emph{in IEEE Transactions on Automatic Control}, vol. 56, no. 8, pp. 1849-1861, Aug. 2011, doi: 10.1109/TAC.2011.2105730.

\bibitem{three_wheel}
Datar, Mandar \& Ketkar, Vishwanath \& Mejari, Manas \& Gupta, Ankit \& Singh, N.M. \& Kazi, Faruk, ``Motion Planning for the Three Wheel Mobile Robot using the Reachable Set Computation under Constraints, (2014)''
\emph{IFAC Proceedings Volumes (IFAC-PapersOnline)}, 3. 10.3182/20140313-3-IN-3024.00178.

\bibitem{mitchell_time_dep_HJ}
I. M. Mitchell, A. M. Bayen and C. J. Tomlin, ``A time-dependent Hamilton-Jacobi formulation of reachable sets for continuous dynamic games,''
\emph{in IEEE Transactions on Automatic Control}, vol. 50, no. 7, pp. 947-957, July 2005, doi: 10.1109/TAC.2005.851439.

\bibitem{evans}
Lawrence C. Evans and Panagiotis E. Souganidis, ``Differential Games and Representation Formulas for Solutions of Hamilton-Jacobi-Isaacs Equations'',
\emph{Indiana University Mathematics Journal (1983), volume 33, pages 773-797}.

\bibitem{new_paper}
Fisac, Jaime, Chen, Mo, Tomlin, Claire, Sastry, Shankar, ``Reach-Avoid Problems with Time-Varying Dynamics, Targets and Constraints (2014)'',
\emph{https://arxiv.org/abs/1410.6445}.

\bibitem{vis_sol}
Crandall, Michael G., and Pierre-Louis Lions, ``Viscosity Solutions of Hamilton-Jacobi Equations'',
\emph{Transactions of the American Mathematical Society, vol. 277, no. 1, American Mathematical Society, 1983, pp. 1–42}.

\bibitem{proof_model}
Nacer Hacene and Boubekeur Mendil, ``Motion Analysis and Control of Three-Wheeled Omnidirectional Mobile Robot'',
\emph{Journal of Control, Automation and Electrical Systems, vol. 30, 2019, pp. 194-213}.

\bibitem{mitch_phd}
Ian Mitchell, ``Application of Level Set Methods to Control and Reachability Problems in Continuous and Hybrid Systems'',
\emph{https://www.cs.ubc.ca/~mitchell/Papers/thesisMitchell.pdf}

\bibitem{LS}
Ian Mitchell, ``A toolbox of level set methods. 2004'',
\emph{http://www.cs.ubc.ca/~mitchell/ToolboxLS}

\bibitem{motion_control}
Xiang Li, Andreas Zell, ``Motion Control of an Omnidirectional Mobile Robot'',
\emph{https://www.scitepress.org/Papers/2007/16448/16448.pdf}

\end{thebibliography}
